\tool

### 2018-04-18 paper/paper.tex
Intro and some related work updates

Although software quality is important, development tools created to improve code are often ignored~\cite{Ivanov2017Gaps}. Previous work explores barriers preventing software engineers from adopting new tools: Tilley and colleagues studied challenges of adopting research-off-the-shelf tools in industry~\cite{Tilley2003ROTS}; Johnson and colleagues reported reasons why software engineers don't use static analysis tools~\cite{Johnson2013Why}; and Xiao and colleagues examined barriers of using security tools to prevent vulnerabilities and malicious attacks~\cite{Xiao2014Security}. One of the main barriers to tool adoption is the discoverability barrier, where users are unaware tools exist~\cite{Murphy-HillScreencastingDiscovery}. Lack of software engineering tool usage can lead to poor code quality, inconvenienced users, and significant amounts of time and money spent fixing errors. Many existing automated approaches have been implemented to increase awareness of software tools and features, but Murphy-Hill and colleagues found that developers prefer learning about tools from colleagues during normal work activities, or \textit{peer interaction}~\cite{MurphyHill2011PeerInteraction}.

To help solve the tool discovery problem among software engineers, we developed an approach for making automated tool recommendations. Our approach integrates characteristics of peer interactions and software engineering practices, and can accomodate many different types of software engineering tools to make customized suggestions to developers. Our technique is based on three main design pillars- \textit{commend}, \textit{apprehend}, and \textit{recommend}. These principles differentiate our approach from existing recommender methods and help improve the effectiveness of automated tool recommendations.

@@

To evaluate our approach, we implemented \tool. Our initial implementation of \tool~for this study recommends \textsc{Error Prone}\footnote{http://errorprone.info}, an open source static analysis tool for Java code, to developers on GitHub\footnote{https://github.com}, a popular code hosting and collaboration website. We measured the effectiveness of our system by observing the frequency of recommendations and how developers reacted to receiving suggestions from our system. This research makes the following contributions:

@@

\section{Related Work}
%TODO: Use related work from whatever conference committee
This work builds on previous research examining recommendation systems in software engineering, techniques for learning new tools, approaches for tool recommendations, and existing automated recommendation systems that recommend software engineering tools.

There are numerous existing technical approaches created to solve the tool discovery problem. Fischer and colleagues found that systems requiring users to explicitly seek help, or passive help systems, are ineffective and active help systems are more useful for increasing tool awareness~\cite{Fischer1984ActiveHelpSystems}. Gordon and colleagues developed Codepourri, a system using crowdsourcing to make recommendations for Python code~\cite{Gordon2015Codepourri}. Linton and colleagues designed a recommender system called OWL (organization-wide learning) to disseminate tool knowledge using logs throughout a company~\cite{Linton2000OWL}. ToolBox was developed as a ``community sensitive help system'' by Maltzahn to recommend Unix commands~\cite{Maltzahn1995Toolbox}. Answer Garden helps users discover new tools based on common questions asked by colleagues~\cite{Ackerman1990AnswerGarden}. SpyGlass automatically recommends tools to help users navigate code~\cite{Viriyakattiyaporn2010Spyglass}. We developed \tool~to actively suggest useful programming tools and increase awareness for software engineers. Our approach differs from existing recommendation systems in the design and implementation of our tool.

>>>>

Although software quality is important, development tools created to improve code quality are often ignored by software engineers~\cite{Ivanov2017Gaps}. Previous work explores barriers preventing software developers from adopting new tools, and researchers have studied challenges to adopting tools for debugging~\cite{CaoDebugging}, static analysis~\cite{Johnson2013Why}, security~\cite{Xiao2014Security}, refactoring~\cite{MurpyHillBarriersRefactoring}, documentation~\cite{ForwardDocumentationRelevance}, and more in their work. One of the main barriers to tool adoption is the discoverability barrier, where users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}. This lack of tool awareness in the software engineering industry can lead to the production of poor-quality applications, inconvenienced users, and significant amounts of time and money spent fixing errors. Many existing automated approaches have been implemented to increase awareness of software tools and features, but Murphy-Hill and colleagues found that developers prefer learning about tools from colleagues during normal work activities, or \textit{peer interactions}~\cite{MurphyHill2011PeerInteraction}.

To help solve the tool discovery problem among software engineers, we developed an approach for making automated tool recommendations. Our approach integrates characteristics of peer interactions and software engineering practices to suggest useful tools to developers. We base our technique on three main design pillars- \textit{commend}, \textit{apprehend}, and \textit{recommend}. These principles differentiate our approach from existing techniques because they can be applied to many different types of software engineering tools and integrate user receptiveness to make customized recommendations to developers.

@@

To evaluate our approach, we implemented \tool. The initial implementation of \tool~for this study recommends \textsc{Error Prone}\footnote{http://errorprone.info}, an open source static analysis tool for Java code, to developers on GitHub\footnote{https://github.com}, a popular code hosting and collaboration website. We measured the effectiveness of our system by observing the frequency of recommendations and how developers reacted to receiving suggestions for tools from our system. This research makes the following contributions:

@@

\section{Related Work}
%TODO: Use related work from whatever conference committee
This project builds on previous research examining the intersection between recommendation systems and software engineering.

Previous research has also studied techniques developers use to learn new information. Piorkowski and colleagues applied Information Foraging Theory to software engineers to determined how developers seek information~\cite{FlemingReactiveInformationForaging}. This research differs from these approaches by presenting and implementing a new technique

Prior work has examined help systems for soft in software engineering.

Researchers have created many different approaches for tool recommendations. Fischer and colleagues found that systems requiring users to explicitly seek help, or passive help systems, are ineffective and active help systems are more useful for increasing tool awareness~\cite{Fischer1984ActiveHelpSystems}.

There are several existing automated approaches created to solve the tool discovery problem among software developers.  Gordon and colleagues developed Codepourri, a system using crowdsourcing to make recommendations for Python code~\cite{Gordon2015Codepourri}. Linton and colleagues designed a recommender system called OWL (organization-wide learning) to disseminate tool knowledge using logs throughout a company~\cite{Linton2000OWL}. ToolBox was developed as a ``community sensitive help system'' by Maltzahn to recommend Unix commands~\cite{Maltzahn1995Toolbox}. Answer Garden helps users discover new tools based on common questions asked by colleagues~\cite{Ackerman1990AnswerGarden}. SpyGlass automatically recommends tools to help users navigate code~\cite{Viriyakattiyaporn2010Spyglass}. We developed \tool~to actively suggest useful programming tools and increase awareness for software engineers. Our approach differs from existing recommendation systems in the design and implementation of our tool.
